Astrophysical calibration of gravitational-wave detectors

### 2015-07-16 docs/cosmic_cal.tex
Added some more to the results section, but it really needs to be checked that what I say is true

>>>>

In figure~\ref{fig:bnsresults} we see slightly different results. Despite the generally higher SNR 
for the \ac{NSBH} systems we find that on averge that the scale factor uncertainty is still roughly 
20\% at distances to 400--500\,Mpc. The range of uncertainty values is also far broader at all 
distances and there is not the plateau and upper limit seen for the \ac{BNS} systems. \MP{This 
needs checked, but ... This broader range of uncertainties appears to be down to the inclusion of 
the spin parameter and correlations this has with the mass ratio $q$ - show posterior examples. The 
lack of an upper plateau seems to be due to the detection criteria having a different effect on the 
distribution of sources that could be seen, in particular it biases the observable sources towards 
having a higher mass ratio (again check this) and thus having more correlation with the spin.}
